\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[sfdefault]{inter}

\definecolor{primary}{HTML}{025940}
\definecolor{linkblue}{HTML}{467886}
\definecolor{bodytext}{HTML}{404040}

\color{bodytext}
\hypersetup{colorlinks=true,urlcolor=linkblue}
\onehalfspacing

\begin{document}
\pagestyle{empty}

\textbf{To:} Mina Drobna $<$mina@bswn.org.uk$>$\\
\textbf{Cc:} Gary Thompson\\
\textbf{Subject:} UnMuseum Developer Proposal - Andrea Enning (via Gary Thompson / Cables and Cameras CIC)

\vspace{1cm}

Dear Mina,

I hope this email finds you well. Gary Thompson kindly introduced me to the UnMuseum Developer opportunity, and I am pleased to submit my proposal for your consideration.

\textbf{About Me}

I am a first generation graduate with a BSc (Hons) ICT from the University of South Wales (2:1, First Class dissertation on RAG architecture). My experience spans:

\begin{itemize}
    \item \textbf{Digital Technical Mentor} at University of South Wales, delivering Microsoft 365 training to students and faculty
    \item \textbf{End User Computing Support} managing Azure Active Directory for 23,000+ users
    \item \textbf{STEM Ambassador} at Technocamps, training educators and students in digital skills
    \item \textbf{Product Coordinator} at PRGRSS mentoring platform (Apple and Android app stores)
\end{itemize}

\textbf{What I Bring to BSWN}

Beyond technical development, I will procure and set up BSWN's Microsoft 365 tenant at no additional cost, including:

\begin{itemize}
    \item Microsoft 365 Business (email, Teams, SharePoint, Office apps)
    \item Azure nonprofit credits (cloud hosting worth \pounds2,800/year)
    \item ElevenLabs Impact Program (voice preservation, 12 months free)
    \item Wazuh security platform (enterprise-grade protection)
\end{itemize}

I have successfully onboarded FirstGens CIC and Nyfasi onto Microsoft nonprofit programmes, securing them over \pounds46,000 in grants and resources.

\textbf{Engagement Structure}

I will be subcontracting under Gary Thompson / Cables and Cameras CIC, ensuring clear accountability and combined expertise in heritage technology. The project will be delivered remotely.

\textbf{Investment}

My proposal totals \textbf{\pounds27,500} for 50 days of work, representing 27-54\% savings compared to G-Cloud framework rates. This includes \pounds14,800 of additional value at no cost.

\textbf{Attached Documents}

\begin{enumerate}
    \item Full Developer Proposal (PDF)
    \item Curriculum Vitae (PDF)
\end{enumerate}

I would welcome the opportunity to discuss this proposal further. Please do not hesitate to contact me or Gary with any questions.

\vspace{1cm}

With warm regards,

\vspace{0.5cm}

\textbf{Andrea Enning}\\
V-Shaped Technical Architect | SFIA Level 5\\
\href{mailto:andiekobbietks@outlook.com}{andiekobbietks@outlook.com}\\
+44 07480 261369\\
\href{https://linkedin.com/in/andiekobbietks}{linkedin.com/in/andiekobbietks}\\
\href{https://github.com/andiekobbietks}{github.com/andiekobbietks}

\end{document}
