\documentclass[11pt,a4paper]{article}

% ============================================
% BSWN UnMuseum Developer Proposal - FINAL
% Andrea Enning - 28 January 2026
% REMOTE DELIVERY | Market-Informed Pricing
% ============================================

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[table]{xcolor}
\usepackage{hanging}
\usepackage[sfdefault]{inter}

% ----- Brand Colours -----
\definecolor{primary}{HTML}{025940}
\definecolor{accentgreen}{HTML}{1DAA61}
\definecolor{linkblue}{HTML}{467886}
\definecolor{bodytext}{HTML}{404040}
\definecolor{lightgrey}{HTML}{F5F5F5}

\color{bodytext}
\hypersetup{colorlinks=true,linkcolor=primary,urlcolor=linkblue,citecolor=primary}
\onehalfspacing

\titleformat{\section}{\Large\bfseries\color{primary}}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\large\bfseries\color{primary}}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\color{accentgreen}}{\thesubsubsection}{0.5em}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{primary}{\small BSWN UnMuseum Developer Proposal}}
\fancyhead[R]{\textcolor{primary}{\small Andrea Enning}}
\fancyfoot[C]{\textcolor{bodytext}{\thepage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{primary}\leaders\hrule height \headrulewidth\hfill}}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\begin{document}

% ----- Title Page -----
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge\bfseries\color{primary} Developer Proposal:\\[0.3cm] UnMuseum Digital Platform\par}
    \vspace{1cm}
    {\Large\color{accentgreen} Black South West Network\par}
    \vspace{2cm}
    {\large\bfseries Submitted by:\par}
    {\Large Andrea Enning\par}
    \vspace{0.5cm}
    {\normalsize\textit{V-Shaped Technical Architect | SFIA Level 5}\par}
    \vspace{0.3cm}
    {\normalsize Subcontracting under \textbf{Gary Thompson}\par}
    {\normalsize\textit{Cables and Cameras CIC, Bristol}\par}
    \vspace{0.5cm}
    {\normalsize\textbf{Delivery Model: Remote}\par}
    \vspace{1cm}
    {\large 28 January 2026\par}
    \vspace{2cm}
    \begin{tabular}{rl}
        \textbf{Email:} & \href{mailto:andiekobbietks@outlook.com}{andiekobbietks@outlook.com} \\[0.3cm]
        \textbf{Telephone:} & +44 07480 261369 \\[0.3cm]
        \textbf{LinkedIn:} & \href{https://linkedin.com/in/andiekobbietks}{linkedin.com/in/andiekobbietks} \\[0.3cm]
        \textbf{GitHub:} & \href{https://github.com/andiekobbietks}{github.com/andiekobbietks} \\
    \end{tabular}
    \vfill
    {\small\textit{Submitted to: Mina Drobna, Operations Director | mina@bswn.org.uk}\par}
\end{titlepage}

\tableofcontents
\newpage

\section{Executive Summary}

I am a first generation graduate and IT professional with deep expertise in web development, cloud infrastructure, and artificial intelligence solutions. I am coming on board as a \textbf{subcontractor under Gary Thompson}, Creative and Cultural Consultant at Cables and Cameras CIC, Bristol. Gary introduced me to this opportunity and will serve as my manager on this project.

This project will be delivered \textbf{remotely}, with collaboration via Microsoft Teams, Slack, and scheduled video calls.

\subsection{The V-Shaped Technical Architect}

\begin{itemize}[leftmargin=*]
    \item \textbf{The Point}: Hard-coded technical delivery (React/TypeScript, Azure, Python)
    \item \textbf{Left Arm}: Peer-reviewed academic prestige (First Class dissertation on RAG architecture)
    \item \textbf{Right Arm}: Proven ecosystem orchestration (InnovateUK, Microsoft, Diana Award organisations)
\end{itemize}

\subsection{Verified Impact: What I Have Secured for Others}

\begin{table}[h]
\centering
\rowcolors{2}{lightgrey}{white}
\begin{tabular}{L{3.5cm}L{2.5cm}L{7cm}}
\toprule
\textbf{\textcolor{primary}{Organisation}} & \textbf{\textcolor{primary}{Value}} & \textbf{\textcolor{primary}{How I Delivered}} \\
\midrule
FirstGens CIC & \pounds46,000+ & Grant intelligence, technical audits, pitch support \\
FirstGens CIC & \pounds3,000/yr & Circle.so platform audit (TCO savings) \\
Nyfasi & \$5,000 & Microsoft Azure AI facility (nonprofit programme) \\
Diversita & Chatbot MVP & AI-powered neurodiversity recruitment assistant \\
PRGRSS/GPE & 4 prototypes & Lovable.dev rapid development \\
Irene Vera Foundation & Website & Co-founder, technical lead \\
\bottomrule
\end{tabular}
\caption{Verified Financial Impact}
\end{table}

\subsection{Live Prototype Portfolio}

All prototypes below are live and can be visited:

\begin{table}[h]
\centering
\rowcolors{2}{lightgrey}{white}
\begin{tabular}{L{3.5cm}L{5cm}L{4.5cm}}
\toprule
\textbf{\textcolor{primary}{Project}} & \textbf{\textcolor{primary}{URL}} & \textbf{\textcolor{primary}{Purpose}} \\
\midrule
FirstGens NavigateU & \href{https://mentor-dynamic-directory.lovable.app/}{mentor-dynamic-directory.lovable.app} & Mentor directory platform \\
GetAway AI & \href{https://getaway-ai-voyage-planner.lovable.app/}{getaway-ai-voyage-planner.lovable.app} & AI travel planning agent \\
PRGRSS Connect & \href{https://prgrss-mentor-connect-02.lovable.app/}{prgrss-mentor-connect-02.lovable.app} & Mentorship matching \\
QuickShip Estimator & \href{https://ship-smart-guess.lovable.app}{ship-smart-guess.lovable.app} & Shipping calculator \\
PRGRSS iOS App & \href{https://apps.apple.com/gb/app/prgrss/id6526481401}{App Store} & Mobile mentorship app \\
\bottomrule
\end{tabular}
\caption{Live Prototype Portfolio}
\end{table}

\section{Technical Approach}

\subsection{What is Microsoft Azure?}

\textbf{Microsoft Azure} is Microsoft's cloud computing platform. It provides:

\begin{itemize}[leftmargin=*]
    \item \textbf{Web hosting}: Servers to run websites and applications without buying physical hardware
    \item \textbf{Database storage}: Secure places to store your data (heritage archives, user accounts)
    \item \textbf{AI services}: Ready-made artificial intelligence tools for search, voice, and image recognition
    \item \textbf{Security}: Enterprise-grade protection for sensitive community data
\end{itemize}

\textbf{Why Azure for BSWN?} Microsoft offers \textbf{free credits for registered nonprofits} through the Microsoft for Nonprofits programme. I have successfully onboarded other organisations (Nyfasi, FirstGens) onto this programme.

\subsection{What I Will Procure and Set Up for BSWN}

As part of this project, I will \textbf{procure, set up, and harden} the following for BSWN at no additional cost:

\begin{table}[h]
\centering
\rowcolors{2}{lightgrey}{white}
\begin{tabular}{L{4cm}L{4cm}R{3cm}}
\toprule
\textbf{\textcolor{primary}{Service}} & \textbf{\textcolor{primary}{What It Does}} & \textbf{\textcolor{primary}{Value}} \\
\midrule
Microsoft 365 Business & Email, Teams, SharePoint, Office apps & \pounds2,500/year \\
Azure Nonprofit Credits & Cloud hosting, databases, AI & \pounds2,800/year \\
Azure Active Directory & Secure user login and identity management & Included \\
Microsoft Teams & Video calls, chat, collaboration & Included \\
SharePoint Online & Document storage and intranet & Included \\
OneDrive for Business & Personal cloud storage for staff & Included \\
\bottomrule
\end{tabular}
\caption{Microsoft 365 Suite Procurement (No Cost to BSWN)}
\end{table}

\subsubsection{Why Can I Do This?}

At the University of South Wales (2023-2024), I served as both \textbf{Digital Technical Mentor} and \textbf{End User Computing Desktop Support}:

\begin{itemize}[leftmargin=*]
    \item Delivered training sessions on \textbf{underutilised Microsoft 365 resources} to students and faculty
    \item Managed \textbf{Azure Active Directory accounts} for 23,000+ users across multiple campuses
    \item Provided hands-on support for \textbf{Microsoft Teams, SharePoint, and OneDrive}
    \item Created documentation guides for \textbf{M365 administration and best practices}
\end{itemize}

\subsection{Platform Architecture: Omeka S}

I propose building on \textbf{Omeka S}, an open-source digital heritage platform actively developed for 10 years (7,078 commits, 33 contributors, v4.2.0 December 2025).

\subsection{Microsoft Heritage: A Precedent}

Microsoft partnered with the \textbf{Universal Hip Hop Museum} in the Bronx to create immersive digital experiences preserving hip hop culture. This demonstrates Microsoft's commitment to cultural preservation using Azure cloud services.

\subsection{ElevenLabs Voice Preservation}

BSWN qualifies for the \textbf{ElevenLabs Impact Program}: 12 months FREE Pro licence (33 million characters, professional voice cloning) for preserving oral histories.

\subsection{Data Sovereignty}

\textbf{BSWN owns and controls all community data}:
\begin{itemize}[leftmargin=*]
    \item Azure UK South region (data never leaves the UK)
    \item Self-hosted database on BSWN's own tenant
    \item Full administrative handover to BSWN staff
\end{itemize}

\subsection{Security: Wazuh Zero Trust}

\textbf{Wazuh} is a free, open-source security platform providing intrusion detection, centralised logging, vulnerability scanning, and GDPR compliance monitoring.

\subsection{Not a Single Point of Failure}

\begin{itemize}[leftmargin=*]
    \item Microsoft engineer review via Partner programme
    \item Comprehensive documentation for future developers
    \item Open-source code BSWN can modify or extend
    \item Full knowledge transfer to BSWN staff
    \item Gary Thompson as ongoing relationship manager
\end{itemize}

\section{Commercial Terms}

\subsection{Engagement Structure}

I will be engaged as a \textbf{subcontractor under Gary Thompson / Cables and Cameras CIC}.

\subsection{IR35 Status and Tax Implications}

\subsubsection{What is IR35?}

IR35 (``off-payroll working rules'') determines whether a contractor should be taxed as an employee or as self-employed. Since April 2017, \textbf{public sector and medium/large private sector clients} are responsible for determining a contractor's IR35 status.

\subsubsection{Status Determination}

BSWN (or Cables and Cameras CIC as the fee-payer) will need to:
\begin{enumerate}[leftmargin=*]
    \item Use HMRC's \textbf{Check Employment Status for Tax (CEST)} tool
    \item Produce a \textbf{Status Determination Statement (SDS)} with reasons
    \item Communicate this determination before the engagement begins
\end{enumerate}

\subsubsection{If Determined ``Inside IR35''}

\begin{itemize}[leftmargin=*]
    \item The fee-payer deducts \textbf{Income Tax and National Insurance} before payment
    \item I receive payment net of tax (similar to an employee)
\end{itemize}

\subsubsection{If Determined ``Outside IR35''}

\begin{itemize}[leftmargin=*]
    \item I invoice through my limited company gross
    \item I manage my own tax affairs through Self Assessment
\end{itemize}

\subsection{My Invoicing and Tax Setup}

\subsubsection{Mettle Business Banking}

\textbf{Mettle} is a free business bank account provided by NatWest:
\begin{itemize}[leftmargin=*]
    \item Professional invoicing from the app
    \item Payment tracking and late payment chasing
    \item Tax pots (automatically set aside percentages for tax)
    \item FSCS protected up to \pounds85,000
\end{itemize}

\subsubsection{FreeAgent Accounting Software}

\textbf{FreeAgent} is HMRC-recognised accounting software that:
\begin{itemize}[leftmargin=*]
    \item Files Self Assessment tax returns \textbf{directly to HMRC}
    \item Is \textbf{Making Tax Digital (MTD) compliant}
    \item Calculates Corporation Tax, VAT, and personal tax automatically
    \item Integrates with Mettle bank feeds
\end{itemize}

\subsubsection{What the Government Requires}

The UK Government requires self-employed individuals to:
\begin{enumerate}[leftmargin=*]
    \item Register for Self Assessment with HMRC
    \item File annual tax returns by 31 January each year
    \item Pay Income Tax and National Insurance on earnings
    \item Keep records for at least 5 years
    \item Comply with Making Tax Digital (digital record-keeping from April 2026)
\end{enumerate}

My Mettle + FreeAgent setup ensures full compliance with all requirements.

\section{Budget and Pricing Justification}

\subsection{G-Cloud 14 Rate Card Comparison}

The \textbf{Skills Framework for the Information Age (SFIA)} is the UK Government standard for IT skills and pricing. Below are published G-Cloud 14 rates:

\begin{table}[h]
\centering
\rowcolors{2}{lightgrey}{white}
\begin{tabular}{L{3cm}C{3.5cm}C{3cm}C{2.5cm}}
\toprule
\textbf{\textcolor{primary}{SFIA Level}} & \textbf{\textcolor{primary}{G-Cloud 14 Range}} & \textbf{\textcolor{primary}{UK Median}} & \textbf{\textcolor{primary}{My Rate}} \\
\midrule
Level 4 (Apply) & \pounds600-950/day & \pounds475/day & \pounds450/day \\
Level 5 (Ensure) & \pounds750-1,200/day & \pounds540/day & \pounds550/day \\
Level 6 (Initiate) & \pounds950-1,500/day & \pounds625/day & \pounds550/day \\
\bottomrule
\end{tabular}
\caption{SFIA Rate Comparison (Sources: G-Cloud 14 Rate Cards, ITJobsWatch Jan 2026)}
\end{table}

\subsection{Why Heritage GRC Work Commands Higher Rates}

This project is not simple web development. It involves:

\begin{itemize}[leftmargin=*]
    \item \textbf{Governance}: Microsoft nonprofit compliance, charity registration requirements
    \item \textbf{Risk Management}: Data sovereignty for sensitive community heritage
    \item \textbf{Compliance}: GDPR, Wazuh security hardening, accessibility (WCAG 2.1 AA)
    \item \textbf{Cultural Sensitivity}: Working with Black and racially minoritised community data
    \item \textbf{Vendor Management}: Microsoft, ElevenLabs, hosting provider negotiations
    \item \textbf{Knowledge Transfer}: Ensuring BSWN is not dependent on a single contractor
\end{itemize}

G-Cloud rates for \textbf{GRC (Governance, Risk, Compliance)} specialists at SFIA Level 5-6 range from \textbf{\pounds950-1,500/day}.

\subsection{Project Costs: \pounds27,500}

\begin{table}[h]
\centering
\rowcolors{2}{lightgrey}{white}
\begin{tabular}{L{6cm}C{1.5cm}C{2cm}C{2cm}}
\toprule
\textbf{\textcolor{primary}{Work Package}} & \textbf{\textcolor{primary}{Days}} & \textbf{\textcolor{primary}{Rate}} & \textbf{\textcolor{primary}{Cost}} \\
\midrule
\textbf{WP1: Discovery and Design} & \textbf{10} & \textbf{\pounds450} & \textbf{\pounds4,500} \\
\quad Community research (RLMT L5) & 3 & \pounds450 & \pounds1,350 \\
\quad Wireframes/UX (HCEV L4) & 3 & \pounds450 & \pounds1,350 \\
\quad Lovable prototypes (PROG L4) & 2 & \pounds450 & \pounds900 \\
\quad Microsoft/ElevenLabs setup (SUPP L5) & 2 & \pounds450 & \pounds900 \\
\midrule
\textbf{WP2: Core Development} & \textbf{15} & \textbf{\pounds550} & \textbf{\pounds8,250} \\
\quad Platform foundation (ARCH L5) & 5 & \pounds550 & \pounds2,750 \\
\quad Authentication (PROG L4) & 4 & \pounds550 & \pounds2,200 \\
\quad Content management (PROG L4) & 4 & \pounds550 & \pounds2,200 \\
\quad Wazuh security (SCTY L5) & 2 & \pounds550 & \pounds1,100 \\
\midrule
\textbf{WP3: Feature Development} & \textbf{15} & \textbf{\pounds550} & \textbf{\pounds8,250} \\
\quad Archive system (PROG L4) & 5 & \pounds550 & \pounds2,750 \\
\quad AI search (PROG L5) & 5 & \pounds550 & \pounds2,750 \\
\quad Voice integration (SINT L4) & 3 & \pounds550 & \pounds1,650 \\
\quad Community features (PROG L4) & 2 & \pounds550 & \pounds1,100 \\
\midrule
\textbf{WP4: Testing and Compliance} & \textbf{5} & \textbf{\pounds550} & \textbf{\pounds2,750} \\
\midrule
\textbf{WP5: Launch and Handover} & \textbf{5} & \textbf{\pounds550} & \textbf{\pounds2,750} \\
\midrule
\textbf{Contingency (5\%)} & -- & -- & \textbf{\pounds1,000} \\
\midrule
\textbf{TOTAL} & \textbf{50 days} & -- & \textbf{\pounds27,500} \\
\bottomrule
\end{tabular}
\caption{SFIA-Based Cost Breakdown}
\end{table}

\subsection{Value Comparison}

\begin{table}[h]
\centering
\begin{tabular}{L{6cm}R{3cm}R{3cm}}
\toprule
\textbf{\textcolor{primary}{Pricing Model}} & \textbf{\textcolor{primary}{50 Days}} & \textbf{\textcolor{primary}{Difference}} \\
\midrule
G-Cloud Level 5 Minimum (\pounds750/day) & \pounds37,500 & -- \\
G-Cloud Level 5 Midpoint (\pounds975/day) & \pounds48,750 & -- \\
G-Cloud Level 5 Maximum (\pounds1,200/day) & \pounds60,000 & -- \\
\midrule
\textbf{My Proposal} & \textbf{\pounds27,500} & \textbf{27-54\% below} \\
\bottomrule
\end{tabular}
\caption{Value Comparison Against G-Cloud Rates}
\end{table}

\subsection{Value Included at No Additional Cost}

\begin{table}[h]
\centering
\rowcolors{2}{lightgrey}{white}
\begin{tabular}{L{8cm}R{3cm}}
\toprule
\textbf{\textcolor{primary}{Included Service}} & \textbf{\textcolor{primary}{Market Value}} \\
\midrule
Microsoft 365 Business tenant setup, hardening, and training & \pounds2,500/year \\
Microsoft nonprofit onboarding and compliance & \pounds2,000 \\
Azure nonprofit credits application & \pounds2,800/year \\
ElevenLabs Impact Program application & \pounds500 \\
Wazuh security platform setup & \pounds3,000 \\
12-month post-launch support & \pounds4,000 \\
\midrule
\textbf{Total Included Value} & \textbf{\pounds14,800} \\
\bottomrule
\end{tabular}
\caption{Services Included at No Additional Cost}
\end{table}

\section{Delivery Model: Remote}

This project will be delivered \textbf{entirely remotely} from Nottinghamshire. Communication will be via:

\begin{itemize}[leftmargin=*]
    \item \textbf{Microsoft Teams}: Video calls, screen sharing, document collaboration
    \item \textbf{Slack}: Day-to-day messaging and quick questions
    \item \textbf{Email}: Formal communications and documentation
    \item \textbf{Scheduled calls}: Weekly progress updates with Gary and BSWN team
\end{itemize}

No travel or accommodation costs are required.

\section{References}

\subsection{Alaya Holloway | CEO, FirstGens UK (Diana Award Winner)}
\textit{Can confirm}: \pounds46,000+ grants secured, \pounds3,000/year Circle.so savings, NavigateU PWA architecture.

\subsection{Agnes Wamagui | Knowledge Transfer Manager, InnovateUK}
\textit{Can confirm}: BYP/InnovateUK partnership convening, national-level ecosystem orchestration.

\subsection{Hope | Founder, Irene Vera Foundation}
\textit{Can confirm}: Co-founder technical work, website development, charity operations support.

\subsection{Gary Thompson | Cables and Cameras CIC, Bristol}
\textit{Relationship}: Introduced me to BSWN; subcontracting partner and project manager.

\subsection{Laura Roberts | Technocamps, University of South Wales}
\textit{Can confirm}: Field operations reliability, crisis management, workshop delivery.

\section{Qualifications}

\begin{itemize}[leftmargin=*]
    \item \textbf{BSc (Hons) ICT} | University of South Wales (2:1, Dissertation: First Class)
    \item \textbf{AWS Cloud Engineering re/Start} | Cardiff and Vale College (2024)
    \item \textbf{DBS Enhanced Check} | Cleared
\end{itemize}

\section{Closing Statement}

The UnMuseum is an extraordinary opportunity to create a living digital space where Black and racially minoritised communities can preserve heritage for future generations.

At \textbf{\pounds27,500}, this proposal represents \textbf{27-54\% savings} compared to G-Cloud framework rates, while including \textbf{\pounds14,800 of additional value} at no cost.

\vspace{1cm}
\textbf{\Large\textcolor{primary}{Let us build something powerful together.}}

\vspace{1cm}
\textbf{Andrea Enning} | 28 January 2026

\newpage
\section{Bibliography}

\hangpara{1.5em}{1}Crown Commercial Service (2024) \textit{G-Cloud 14 Framework Agreement RM1557.14}. Available at: https://www.crowncommercial.gov.uk/agreements/RM1557.14l4 (Accessed: 28 January 2026).

\hangpara{1.5em}{1}ElevenLabs (2025) \textit{Impact Program for Nonprofits}. Available at: https://elevenlabs.io/impact-program (Accessed: 28 January 2026).

\hangpara{1.5em}{1}FreeAgent (2025) \textit{Self Assessment Tax Return Filing}. Available at: https://www.freeagent.com/features/self-assessment/ (Accessed: 28 January 2026).

\hangpara{1.5em}{1}GOV.UK (2024) \textit{Understanding off-payroll working (IR35)}. Available at: https://www.gov.uk/guidance/understanding-off-payroll-working-ir35 (Accessed: 28 January 2026).

\hangpara{1.5em}{1}ITJobsWatch (2026) \textit{SFIA Contract Job Trends and Contractor Rates}. Available at: https://www.itjobswatch.co.uk/contracts/uk/sfia.do (Accessed: 28 January 2026).

\hangpara{1.5em}{1}Mettle by NatWest (2025) \textit{Business Bank Account}. Available at: https://www.mettle.co.uk/ (Accessed: 28 January 2026).

\hangpara{1.5em}{1}Microsoft (2019) `Breaking New Sound: The Hip Hop Museum'. Available at: https://unlocked.microsoft.com/the-hip-hop-museum/ (Accessed: 28 January 2026).

\hangpara{1.5em}{1}Omeka (2025) \textit{Omeka S Documentation}. Available at: https://omeka.org (Accessed: 28 January 2026).

\hangpara{1.5em}{1}Qdos Contractor (2025) \textit{Which expenses can contractors claim when working inside IR35?}. Available at: https://www.goqdos.com/ir35/which-expenses-can-contractors-claim-when-working-inside-ir35 (Accessed: 28 January 2026).

\hangpara{1.5em}{1}SFIA Foundation (2024) \textit{SFIA 9: Skills Framework for the Information Age}. Available at: https://sfia-online.org (Accessed: 28 January 2026).

\hangpara{1.5em}{1}Wazuh (2025) \textit{Open Source Security Platform}. Available at: https://wazuh.com (Accessed: 28 January 2026).

\end{document}
